\bf Calendar-based graphics for visualizing people's daily schedules

### 2018-10-22 main.Rmd
done with example section
make smart meter calendar displays into 4 separate plots

```{r h12, fig.height = 10, fig.cap = "Calendar displays for household 1 and 2. It reveals their regular tendency of using air conditioning and heating and vacation time periods. For example, household 2 leaves heating on consecutively in the mid July, is on holiday for Christmas and the second week of June."}
```

```{r h34, fig.height = 10, fig.cap = "Calendar displays for household 3 and 4. Household 3 are on long trips twice in the past year, while household 4 takes three short trips in October, December, and June. Both households leave no clue if they use air conditioning and heating."}
```

>>>>

```{r h1, fig.height = 5, fig.cap = "Calendar displays for household 1. They tend to use air conditioning in the late afternoon untill the mid-night in summer. It seems that they are on vacation in June."}
```

```{r h2, fig.height = 5, fig.cap = "Calendar displays for household 2. It reveals their regular tendency of using air conditioning and heating, and vacation periods. They leaves heating on consecutively in the mid July, is on holiday for Christmas and the second week of June."}
```

```{r h3, fig.height = 5, fig.cap = "Calendar displays for household 3. Their energy use reveals different behaviors between summer and winter: only one peak in most summer days, while two peaks in winter. They are on long trips twice in the past year."}
```

```{r h4, fig.height = 5, fig.cap = "Calendar displays for household 4. Energy are heavily used in the evening for household 4. They also take three short trips in October, December, and June."}
```

### 2018-10-22 main.tex
make smart meter calendar displays into 4 separate plots

{\centering \includegraphics[width=\textwidth]{figure/h12-1}

@@

\caption{Calendar displays for household 1 and 2. It reveals their regular tendency of using air conditioning and heating and vacation time periods. For example, household 2 leaves heating on consecutively in the mid July, is on holiday for Christmas and the second week of June.}\label{fig:h12}
\end{figure}

@@

{\centering \includegraphics[width=\textwidth]{figure/h34-1}

@@

\caption{Calendar displays for household 3 and 4. Household 3 are on long trips twice in the past year, while household 4 takes three short trips in October, December, and June. Both households leave no clue if they use air conditioning and heating.}\label{fig:h34}
\end{figure}

>>>>

{\centering \includegraphics[width=\textwidth]{figure/h1-1}

@@

\caption{Calendar displays for household 1. They tend to use air conditioning in the late afternoon untill the mid-night in summer. It seems that they are on vacation in June.}\label{fig:h1}
\end{figure}

@@

{\centering \includegraphics[width=\textwidth]{figure/h2-1}

@@

\caption{Calendar displays for household 2. It reveals their regular tendency of using air conditioning and heating, and vacation periods. They leaves heating on consecutively in the mid July, is on holiday for Christmas and the second week of June.}\label{fig:h2}
\end{figure}

{\centering \includegraphics[width=\textwidth]{figure/h3-1}

\caption{Calendar displays for household 3. Their energy use reveals different behaviors between summer and winter: only one peak in most summer days, while two peaks in winter. They are on long trips twice in the past year.}\label{fig:h3}
\end{figure}

{\centering \includegraphics[width=\textwidth]{figure/h4-1}

\caption{Calendar displays for household 4. Energy are heavily used in the evening for household 4. They also take three short trips in October, December, and June.}\label{fig:h4}
\end{figure}
